Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-25 fmics/paper.tex
Clarify definition of RS in Table 1

\begin{table}[t]
\caption{
Descriptions of the HOL functions comprising our model of the SRS structure.
\label{tab:descriptions}
}
\begin{tabular}{lp{0.8\textwidth}}
Function&Intended meaning\\
\hline\\
\(\mathsf{tap}\;n\;x\)&The position of tap $x$ of slice $n$.\\
\(\mathsf{input}\;n\)&A pair $(n',x)$ indicating that the input to slice $n$ is output $x$ of slice $n'$.\\
\(\mathsf{delay}\;n\)&The number of time steps between updates of slice $n$.\\
\(\mathsf{source}\;D\;n\;m\;t\)&The value of the cell that is the direct input to cell $m$ of slice $n$, at time $t$, given input stream $D$.\\
\(\mathsf{SR}\;D\;n\;m\;t\)&The value of cell $m$ of shift register $n$, at time $t$, given input stream $D$.\\
\(\mathsf{output}\;D\;n\;x\;t\)&The value of output $x$ of slice $n$, at time $t$, given input stream $D$.\\
\(\mathsf{RS}\;D\;n\;t\)&The value of Running Sum slice (?) $n$ at time $t$, given input stream $D$.\\
\(\mathsf{update\_time}\;n\;t\)&A boolean indicating whether $t$ is an update time for slice $n$.
\end{tabular}
\end{table}

>>>>

\begin{table}[t]
\caption{
Descriptions of the HOL functions comprising our model of the SRS structure.
\label{tab:descriptions}
}
\begin{tabular}{lp{0.8\textwidth}}
Function&Intended meaning\\
\hline\\
\(\mathsf{tap}\;n\;x\)&The position of tap $x$ of slice $n$.\\
\(\mathsf{input}\;n\)&A pair $(n',x)$ indicating that the input to slice $n$ is output $x$ of slice $n'$.\\
\(\mathsf{delay}\;n\)&The number of time steps between updates of slice $n$.\\
\(\mathsf{source}\;D\;n\;m\;t\)&The value of the cell that is the direct input to cell $m$ of slice $n$, at time $t$, given input stream $D$.\\
\(\mathsf{SR}\;D\;n\;m\;t\)&The value of cell $m$ of shift register $n$, at time $t$, given input stream $D$.\\
\(\mathsf{output}\;D\;n\;x\;t\)&The output at tap $x$ of slice $n$, at time $t$, given input stream $D$.\\
\(\mathsf{RS}\;D\;n\;t\)&The $n$-th running sum at time $t$, given input stream $D$.\\
\(\mathsf{update\_time}\;n\;t\)&A boolean indicating whether $t$ is an update time for slice $n$.
\end{tabular}
\end{table}
